Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/related.tex
Update on Overleaf.

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, and COO.
%
Examples include Scipy, PETSc, Armadillo, and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, eigenweb}.

>>>>

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, and COO.
%
Examples include Scipy, PETSc, Armadillo, and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, eigenweb}.
%
Several of these libraries also feature some graph or mesh algorithms built on sparse matrices, which represent other sparse structures.
%
GraphBlas perhaps exemplifies this pattern with support for many sparse matrix operations on a variety of formats~\cite{kepner2016mathematical} although a variety of other graph libraries adopt a similar approach such as LAgraph~\cite{mattson2019lagraph}
